The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 Finally, \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
 in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
 can also be realized by oblique jets as the eROSITA bubbles.\

>>>>

 \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux with a CRe power-law index 2.4\
 compared with the observed one\
 in the energy bin $76.8-153.6$ GeV.\
 As the eROSITA bubbles,\
 one can see that the symmetric of the \textit{Fermi} bubbles\
 can also be realized by oblique jets.\

 Finally, the comparison between \Cref{fig__jetI5+ismSeed3-45deg-CR} and\
 \Cref{fig__jetI5+ismSeed3-45deg} shows that the CR pressure\
 is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure by a factor 10--20.\
 We thefore stress that in \Cref{governing-eq},\
 assuming $p_{CR}\ll p_{\text{gas}}$ is resonable.
